Matching Bullets

### 2015-12-09 imaging-paper.Rnw
fiddling with figure placement

\subsection{Varying crosscuts}
The crosscut at which a comparison is done matters -- as crosscuts are further apart, more pronounced differences between the crosscuts show up. This poses both a caveat to matching attempts as well as an opportunity: on the one hand we have to be aware of which crosscut level was used in a matching, but on the other hand we can use multiple crosscuts of the same bullet for an initial assessment of its quality.Both of these situations are assessed and discussed in more detail below: 
Figure~\ref{fig:crosscuts} shows a sequence of crosscuts for bullet land 1-5 (barrel 1) that are taken 50$\mu m$ apart, between 150$\mu m$  and 450$\mu m$. These  are compared to a crosscut at 100$\mu m$. Initially this comparison constitutes an almost perfect match (consolidated by a CMS of fourteen) between the two crosscuts. However, the match quickly deteriorates with increasing distance to non-matches at a crosscut of $x = 300\mu m$ or higher.  Only if the crosscut is within 150$\mu m$ do we get a good visual match even when we know that the same bullet surface is being used. 
Given that we have to expect some variation in nominally the same crosscut levels due to manual alignments in microscopes, we should take crosscut levels into account in the automatic matching routine by evaluating matches at several cross sections. 
\begin{figure}[hbtp]
<<crosscuts-vary, echo=FALSE, fig.width = 7, fig.height = 14, out.width = '\\linewidth', cache=TRUE, warning = FALSE>>=
paths <- file.path(datadir, dir(datadir))
crosscuts <- seq(100, 450, by = 50)
lof <- processBullets(paths[5], x = crosscuts)
lof$bullet <- paste(lof$bullet, lof$x)

@@

grid.arrange(lop[[1]], lop[[2]], lop[[3]], lop[[4]], lop[[5]], lop[[6]], 
             lop[[7]],
             ncol = 1)
@
\caption{\label{fig:crosscuts}Overview of the variations in the surface along different crosscuts. Crosscut at $x = 100$ is compared to crosscuts every 50$\mu m$. With every step away from the original crosscut site, the number of differences between the crosscuts increases, and the number of maximum CMS decreases from initially 14 to  3 or fewer at $x = 300\mu m$ and higher. }
\end{figure}
\afterpage{\clearpage}

@@

grid.arrange(lop[[1]], lop[[2]], lop[[3]], 
             lop[[4]], lop[[5]], 
             ncol=1)
@
\caption{\label{fig:crosscuts2}Varying crosscuts for barrel 3, bullet 1. Initially, the match between crosscuts 25$\mu m$ apart is affected strongly by break off at the bottom of the bullet. At a crosscut level of $175\mu m$ the bullet pattern stabilizes. For this land, matches should not be attempted at lower crosscuts.}
\end{figure}

>>>>

\subsection{Varying crosscuts}
The crosscut at which a comparison is done matters -- as crosscuts are further apart, more pronounced differences between the crosscuts show up. This poses both a caveat to matching attempts as well as an opportunity: on the one hand we have to be aware of which crosscut level was used in a matching, but on the other hand we can use multiple crosscuts of the same bullet for an initial assessment of its quality. Both of these situations are assessed and discussed in more detail below: 
Figure~\ref{fig:crosscuts} shows a sequence of crosscuts for bullet land 1-5 (barrel 1) that are taken 50$\mu m$ apart, between 150$\mu m$  and 450$\mu m$. These  are compared to a crosscut at 100$\mu m$. Initially this comparison constitutes an almost perfect match (consolidated by a CMS of fourteen) between the two crosscuts. However, the match quickly deteriorates with increasing distance to non-matches at a crosscut of $x = 300\mu m$ or higher.  Only if the crosscut is within 150$\mu m$ do we get a good visual match even when we know that the same bullet surface is being used. 
Given that we have to expect some variation in nominally the same crosscut levels due to manual alignments in microscopes, we should take crosscut levels into account in the automatic matching routine by evaluating matches at several cross sections. 
\begin{figure}[hbtp]
<<crosscuts-vary, echo=FALSE, fig.width = 7, fig.height = 14, out.width = '\\linewidth', cache=TRUE, warning = FALSE>>=
paths <- file.path(datadir, dir(datadir))
crosscuts <- seq(100, 450, by = 50)
lof <- processBullets(paths[5], x = crosscuts)
lof$bullet <- paste(lof$bullet, lof$x)

@@

grid.arrange(lop[[1]], lop[[2]], lop[[3]], lop[[4]], lop[[5]], lop[[6]], 
             lop[[7]],
             ncol = 1)
@
\caption{\label{fig:crosscuts}Overview of the variations in the surface along different crosscuts. Crosscut at $x = 100$ is compared to crosscuts every 50$\mu m$. With every step away from the original crosscut site, the number of differences between the crosscuts increases, and the number of maximum CMS decreases from initially 14 to  3 or fewer at $x = 300\mu m$ and higher. }
\end{figure}
%\afterpage{\clearpage}

@@

grid.arrange(lop[[1]], lop[[2]], lop[[3]], 
             lop[[4]], lop[[5]], 
             ncol=1)
@
\caption{\label{fig:crosscuts2}Varying crosscuts for barrel 3, bullet 1. Initially, the match between crosscuts 25$\mu m$ apart is affected strongly by break off at the bottom of the bullet. At a crosscut level of $175\mu m$ the bullet pattern stabilizes. For this land, matches should not be attempted at lower crosscuts.}
\end{figure}
\afterpage{\clearpage}
